\documentclass[12pt]{letter}               % letter class, 12 points
\address{555 Main St.\\Sometown, NY 12345} % Return address
\signature{My Name\\My Title}              % Name for signature
\begin{document}                           % End of preamble
\begin{letter}{Mr.~Smith\\ President,      % Begin letter by giving
   Big Name Co.\\Bigburg, MI 45678}        %   recipient’s address
\opening{Dear Mr.~Smith:}                  % Name for salutation
Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. Some matter. 
\closing{Sincerely,} % Format for the closing.
                     % The name is taken from
                     % \signature command above.
\cc{My Boss}         % Name(s) of those
                     % receiving copies
\end{letter}         % End of letter
\end{document}       % The required last line
